Estimating the genome-wide contribution of selection to temporal allele frequency change

### 2020-05-01 manuscript/manuscript.tex
ms updates

Note about fixations

@@

  \caption{The temporal covariances, $\cov(\Delta p_{50}, \Delta p_t)$ (where $t$
    varies along the x-axis) created by background selection. Unlike
    directional selection figures, where we choose the reference generation to
    be the first generation after the onset of selection, here we choose an
    arbitrary reference generation (generation 50). The symmetry of temporal
    covariance around the reference generation, is expected, since unlike
    directional selection the level of additive genetic variance for fitness has
    hit mutation-selection-drift balance.}

@@

@@

\subsubsection{The Effect of Fixations}

>>>>

@@

  \caption{The temporal covariances, $\cov(\Delta p_{50}, \Delta p_t)$ (where
    $t$ varies along the x-axis) created by background selection, under
    different recombination rates ($r_{BP}$, rows), selection coefficients
    ($s$), and deleterious mutation rates ($U$). Unlike directional selection
    figures, where we choose the reference generation to be the first
    generation after the onset of selection, here we choose an arbitrary
    reference generation (generation 50). The symmetry of temporal covariance
    around the reference generation, is expected, since unlike directional
    selection the level of additive genetic variance for fitness has hit
    mutation-selection-drift balance. Note that the first column sets constant
  $U = 1.0$, and $s$ varies, while the second column sets $s=0.05$ constant,
and varies $U$.}

@@

  \caption{The trajectories of $G(t)$ through time under background selection,
    under different recombination rates ($r_{BP}$, rows), selection
    coefficients ($s$), and deleterious mutation rates ($U$). The first column
    sets $U = 1.0$, and $s$ varies, while in the second column $s=0.05$ is held
  constant, and $U$ varies.}

Note that to investigate whether different selection coefficients converged to
the same levels of $G(t)$, we extended the number of generations we calculated
our statistics on (e.g. in earlier exponential and Gaussian stabilizing
selection fitness function, these were calculated to fifty generations; here
we've calculated them to one hundred generations). This lead us to discover a
subtle bias temporal covariance: whether sites that fix or are lost through
time are included or excluded in the temporal covariance calculation can lead
to biases in temporal covariance. We discuss this extensively in the next
section, Supplementary Materials Section \ref{supp:fixation}, but here we note
that all the background selection results exclude fixed and lost sites; these
are marked as missing and excluded from the temporal covariance and $G(t)$
calculations.

\begin{figure}[!ht]
  \centering
  \includegraphics[width=\textwidth]{figures/fig-bgs-convergence-correlation.pdf}

@@

  \label{suppfig:supp-bgs-converg}
\end{figure}

\subsubsection{The Effect of Fixations}
\label{supp:fixation}
